Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2022-02-10 paper/paper.tex
More WIP

Considering just one receptor-ligand pair,
for instance $r_0$/$l_0$, and defining their interaction as repulsive, an axon
from the transverse side of the retina, which expresses a high level of
receptor $r_0$ will interact most strongly with an axon from the nasal side of
the retina, where $l_0$ is most highly expressed. The interaction with axons
that originate nearby, on the transverse side will be minimal, as these
express low levels of $l_0$. Axons originating from the nasal side of the
retina interact weakly with axons originating nearby.

>>>>

Considering just one receptor-ligand pair, for instance $r_0$/$l_0$, and
defining their interaction as repulsive, an axon from the transverse side of
the retina, which expresses a high level of receptor $r_0$ will interact most
strongly with an axon from the nasal side of the retina, where $l_0$ is most
highly expressed. The interaction with axons that originate nearby, on the
transverse side will be minimal, as these express low levels of $l_0$. Axons
originating from the nasal side of the retina also interact most strongly with
axons originating nearby and in general the $r_0$/$l_0$ interaction is weaker
between a nasal axon and a second retinal axon. However, when the opposing
receptor/ligand pair ($r_2$/$l_2$) interaction is summed with that of
$r_0$/$l_0$, a more even interaction is found, with interactions between axons
from extreme sides of the retina being the strongest. (Poss.~supp.~figure
based on the Octave script J.m).

We performed the same simulated annealing process as for the
$\mathbf{GC}$-model to find the parameters best able to recover the wildtype
pattern and found $m_{\!_G} = 0.00047$, $m_{\!_J} = 0.00089$ and $r_{\!_J} = 0.341$.
